Local Search Approximation Algorithms for Clustering

### 2015-04-24 tex/presentation/presentation.tex
Optimal Solutions
Calculated for all values of k except for pmed35 - pmed40 which are too
slow

\begin{frame}
\frametitle{Motivation}
Look for structure in unlabeled data.
\begin{itemize}
\item Social networks
\item Handwritten letters
\item Grouping customer classes
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{$k$-Means Algorithm and Local Search}
Objective: partition the data into sets $S_1, S_2, \ldots, S_k$ with means $\mu_1, \ldots, \mu_k$ to minimize $\sum_{i=1}^k \sum_{x \in S_i} ||x-\mu_i||^2$.

>>>>

\begin{frame}
\frametitle{Motivation}
Look for structure in unlabeled data.
\begin{itemize}
\item Group plants by species
\item Find similar gene sequences to find gene families across species
\item Infer population structures
\item Crime analysis
\item PET scans to differentiate different tissues
\item Social networks and recognizing communities
\item Image segmentation and object regonition
\item Grouping customer classes and market segmentation
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{$k$-Means Algorithm}
Objective: partition the data into sets $S_1, S_2, \ldots, S_k$ with means $\mu_1, \ldots, \mu_k$ to minimize $\sum_{i=1}^k \sum_{x \in S_i} ||x-\mu_i||^2$.
